`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-01-10 inst/manuscript/manuscript.rmd
Fix typos;

# Input Data and Data Processing {-}
To analyse raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information on the path to the 
fluorimeter--generated spectrum, the amount of protein reconstituted into
proteoliposomes, the assay volume before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lipids 
present (to calculate a protein to phospholipid ratio or PPR) etc. The user 
supplies this information in a spreadsheet (see below for supporting 
functionality).

@@

With `flippant` we present an integrated solution for data analysis in the 
context of dithionite scramblase assays. Requiring only basic familiarity with 
`R` as an environment for statistical computing and graphics 
[@r_core_team_r:_2016], scientists can quickly analyse such data and arrive at 
publication--grade graphics that offer extensive facilities for individual 
optimization and adaptation [@wickham_ggplot2_2009]. On a laptop system with 
`r parallel::detectCores()` cores and 8 GB RAM (no SSD), running `Linux` and 
`R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
statements generating equivalents to the plots and calculations presented here
take a mere `r analysis_timing_median` seconds (median; 
$\text{MAD}=`r analysis_timing_mad`~\text{s}$; $n=`r analysis_timing_n`$).

@@

`flippant`, in conclusion, provides means for quick, reproducible data analysis
in the context of scramblase activity analysis and a platform for review, 
dissemination and extension of the strategies it employs. As BSA--back 
extraction, a different assay for lipid translocation across liposome bilayers
[@kubelt_transbilayer_2002;@vehring_flip-flop_2007], can utilize an essentially 
identical data analysis workflow, `flippant` is expected to facilitate analysis
of such experiments as well.

@@

```{r figure2-creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
figure2_plot %<>% multipanelfigure::add_panel(
  top_panel = 1,
  panel = flippant::scramblase_assay_plot(template_file) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])))
figure2_plot %<>% multipanelfigure::add_panel(
  top_panel = 2,
  panel = flippant::scramblase_assay_plot(template_file, split_by_experiment = FALSE) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])) +
    ggplot2::facet_wrap(c("`Experimental Series`"))+
    ggplot2::guides(colour = "none"))
grid::rectGrob(
    width = grid::unit(0.1, "mm"),
    height = grid::unit(0.1, "mm")) %>%
  grid::grid.draw()
```

>>>>

# Input Data and Data Processing {-}
To analyze raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information on the path to the 
fluorimeter--generated spectrum, the amount of protein reconstituted into
proteoliposomes, the assay volume before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lipids 
present (to calculate a protein to phospholipid ratio or PPR) etc. The user 
supplies this information in a spreadsheet (see below for supporting 
functionality).

@@

With `flippant` we present an integrated solution for data analysis in the 
context of dithionite scramblase assays. Requiring only basic familiarity with 
`R` as an environment for statistical computing and graphics 
[@r_core_team_r:_2016], scientists can quickly analyze such data and arrive at 
publication--grade graphics that offer extensive facilities for individual 
optimization and adaptation [@wickham_ggplot2_2009]. On a laptop system with 
`r parallel::detectCores()` cores and 8 GB RAM (no SSD), running `Linux` and 
`R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
statements generating equivalents to the plots and calculations presented here
take a mere `r analysis_timing_median` seconds (median; 
$\text{MAD}=`r analysis_timing_mad`~\text{s}$; $n=`r analysis_timing_n`$).

@@

`flippant`, in conclusion, provides means for quick, reproducible data analysis
in the context of scramblase activity analysis and a platform for review, 
dissemination and extension of the strategies it employs. As BSA--back 
extraction, a different assay for lipid translocation across liposome bilayers
[@kubelt_transbilayer_2002;@vehring_flip-flop_2007], can utilize an essentially 
identical data analysis work flow, `flippant` is expected to facilitate analysis
of such experiments as well.

@@

```{r figure2-creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconstitution."}
figure2_plot %<>% multipanelfigure::add_panel(
  top_panel = 1,
  panel = flippant::scramblase_assay_plot(template_file) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])))
figure2_plot %<>% multipanelfigure::add_panel(
  top_panel = 2,
  panel = flippant::scramblase_assay_plot(template_file, split_by_experiment = FALSE) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])) +
    ggplot2::facet_wrap(c("`Experimental Series`"))+
    ggplot2::guides(colour = "none"))
grid::rectGrob(
    width = grid::unit(0.1, "mm"),
    height = grid::unit(0.1, "mm")) %>%
  grid::grid.draw()
```
